Title

### 2020-12-03 documents/DraftReport.Rmd
to-dos

>>>>

To-do's

Presentation
- caroline/amelia

Write-up
- intro (amanda re-reads and checks for possible additions)
- methods/equation check: change YOTY to juv (hannah)
- results (abby/hannah)

- discussion (TBD)
-- summarize high-level finding

-- why we think we see what we see
--- crux of the issue.... 
(1) how the life cycle model relies on different data sources
(2) parameter identifiability
(3) ?

-- limitations/caveats of this particular study (what can/can't we make inference to/about)
--- life histories

-- future directions
--- degrading quantity/quality

-- importance of the work
(1) understanding IPMs better
(2) understanding weaknesses of IPMs: when does the integration almost hurt instead of help?
(3) survey design

Figures/analysis/etc
- posterior densities (amanda)
- life cycle/survey timing diagram (amelia)
- figure captions/printing (amanda)
- 3 dags (amelia)

Code review
- annotate data simulation (amanda! caroline! amelia!)

Displaying results
- posterior densities
- table (true values, data included, posterior mean, 95% CI, mean bias, mean RMSE)
